---
title: "Using XGBoost for Fraud Detection"
author: "Mu Niu, Yixin Xue, Amber Wang, David Lin, Qifei Cui"
date: "2023-12-08"
output: html_document
---

```{r}
library(tidymodels)
library(xgboost)
library(tidyverse)
library(pROC)
library(ggplot2)
```

## Abstract

XGBoost, an acronym for eXtreme Gradient Boosting, was crafted by Dr. Tianqi Chen in 2016 as a gradient-boosting algorithm. Demonstrating remarkable success, it has emerged as a formidable player in various data science competitions. Renowned for its exceptional performance, XGBoost stands out as a robust solution for tasks such as handling structured data, text classification, regression, and notably, exhibiting superior capabilities on large-scale datasets. Our vignette presents a comprehensive exploration of XGBoost, including its mathematical principles, programming language support, and practical application in classification problems.

```{r cars}
summary(cars)
```

## Dataset Introduction

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.

## Exploratory Data Analysis

## Data Preprocessing

## Introduction to Boosted Trees and XGBoost

## Fraud Detection with XGBoost in R

## Results and Analysis
